Multi-Source Debiased Calibration Simulation

### 2024-05-13 final/reports/prelim_paper.tex
Fixed multisource simulation 2. It works, but I need to change the estimator to be a GLS estimate instead of a simple average.

where $\hat T = (\hat{\bf X}^{(m)}, \sum_{i \in U} g(d_{im}) q_i)^T$ and $d_{im}$
are the design weights for $A_m$.

@@

@@

@@

\appendix

\section{Derivation of the Estimated Variance of DC-Pop in Simulation 1}

We know that $\hat Y_{DC-Pop} = \sum_{i \in A_2} w_{1i} \hat w_{2i|1}(\hat
\lambda) y_i$ where $\hat w_{2i|1}$ solves

  \begin{equation}
    \argmin_{w_{2|1}} \sum_{i \in A_2} \frac{1}{\pi_{1i}} G(w_{2i})
    \text{ such that}
    \sum_{i \in A_2} w_{1i} w_{2i|1} z_i = \sum_{i \in U} z_i.
  \end{equation}

This means that using the technique of \cite{randles1982asymptotic},
the linearization of $\hat Y_{DC-Pop}$ is

$$\hat Y_{DC-Pop, \ell} = \sum_{i \in A_2} w_{1i} \hat w_{2i|1}(\hat \lambda) y_i + 
\left( \sum_{i \in U} z_i - 
\sum_{i \in A_2} w_{1i} w_{2i|1}(\hat \lambda) z_i \right) \phi.$$

Since $\phi^*$ satisfies $E\left[\frac{\partial}{\partial \lambda} \hat Y_{DC-Pop,
\ell}(\lambda^*, \phi^*)\right] = 0$, $\phi^*$ is the same as it is for $\hat Y_{DC-Est,
\ell}$ with $q_i = 1$,

  \begin{align*}
    \phi^*
    &= E\left[\sum_{i \in A_2} \frac{w_{1i}z_i z_i^T }{g'(d_{2i|1})}\right]^{-1}
    E\left[\sum_{i \in A_2} \frac{w_{1i}z_i y_i}{g'(d_{2i|1})}\right]\\
    &= \left[\sum_{i \in U} \frac{\pi_{2i|1}z_i z_i^T}{g'(d_{2i|1})}\right]^{-1}
    \left[\sum_{i \in U} \frac{\pi_{2i|1} z_i y_i}{g'(d_{2i|1})}\right].\\
  \end{align*}

Hence,

$$
\hat Y_{DC-Pop, \ell} = \sum_{i \in U} z_i \phi^* + \sum_{i \in A_2} w_{1i} \hat
w_{2i|1}(\lambda^*) (y_i - z_i \phi^*).
$$

Unlike the two-phase regression estimator and $\hat Y_{DC-Est}$ this
linearization only has uncertainty in the second term. The first term is a
population estimate. Let $\varepsilon_i = (y_i - z_i \phi^*)$. This means that

\begin{align*}
  V(\hat Y_{DC-Pop, \ell}) 
  &= V(E[\hat Y_{DC-Pop, \ell} \mid A_1]) + E[V(\hat Y_{DC-Pop, \ell} \mid A_1)] \\
  &= V\left(\sum_{i \in A_1} w_{1i} \pi_{2i|1} \hat w_{2i|1}(\lambda^*)
  \varepsilon_i\right) + 
  E\left[\sum_{i \in A_1} \pi_{2i|1}(1 - \pi_{2i|1}) w_{1i}^2 \hat w_{2i|1}(\lambda^*)^2
    \varepsilon_i^2 \right]\\
  &= \sum_{i \in U} \pi_{1i}(1 - \pi_{1i}) w_{1i}^2 \pi_{2i|1}^2 
  \hat w_{2i|1}(\lambda^*)^2 \varepsilon_i^2 +
  \sum_{i \in U} \pi_{1i}\pi_{2i|1}(1 - \pi_{2i|1}) w_{1i}^2 \hat w_{2i|1}(\lambda^*)^2
    \varepsilon_i^2\\
  &= \sum_{i \in U} w_{1i} w_{2i|1}(\lambda^*)^2 \pi_{2i|1}
  ((1 - \pi_{1i})\pi_{2i|1} + (1 - \pi_{2i|1})) \varepsilon_i^2.
\end{align*}

Since $w_{2i|1}(\lambda^*) \pi_{2i|1} = 1$, there are two potential estimators
of the variance,

\begin{align*}
  \hat V_1 &= \sum_{i \in A_2} w_{1i}^2 w_{2i|1}(\hat \lambda)^2 
  ((1 - \pi_{1i})\pi_{2i|1} + (1 - \pi_{2i|1})) \varepsilon_i^2\\
  \hat V_2 &= \sum_{i \in A_2}  w_{1i}^2 d_{2i|1}^2
  ((1 - \pi_{1i})\pi_{2i|1} + (1 - \pi_{2i|1})) \varepsilon_i^2.
\end{align*}

In the current simulation, we use $\hat V_1$, but I have tried $\hat V_2$ and
the results are similar.
\end{document}

>>>>

where $\hat T = (\hat{\bf X}^{(A_m)}, \sum_{i \in U} g(d_{im}) q_i)^T$ and $d_{im}$
are the design weights for $A_m$.

@@

We first run a simulation for the case in which we only have one sample in which
we observe $Y$. We have the following superpopulation model with $N=10000$
elements:

$$
\begin{aligned}
X_{1i} &\stackrel{ind}{\sim} N(2, 1) \\
X_{2i} &\stackrel{ind}{\sim} Unif(0, 4) \\
X_{3i} &\stackrel{ind}{\sim} N(0, 1) \\
Z_i &\stackrel{ind}{\sim} N(0, 1) \\
\varepsilon_i &\stackrel{ind}{\sim} N(0, 1) \\
Y_{i} &= 3 X_{1i} + 2 X_{2i} + \varepsilon_i \\
\pi_{0i} &= \min(\max(\Phi(-x_{1i}), 0.02), 0.9)\\
\pi_{1i} &= n_1 / N.\\
\pi_{2i} &= \Phi(x_{2i} - 2) \\
\end{aligned}
$$

We observe the following columns in each sample

\begin{table}[ht!]
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    Sample & $X_1$ & $X_2$ & $X_3$ & $Y$ \\
    \midrule
   $A_0$  & \checkmark     & \checkmark     & \checkmark     &  \checkmark \\    
   $A_1$  & \checkmark     &       & \checkmark     &    \\  
   $A_2$  & \checkmark     & \checkmark     &       &    \\  
   \bottomrule
  \end{tabular}
\end{table}

For the sampling mechanism both $A_0$ and $A_1$ are selected using a Poisson
sample with response probabilities $\pi_{0i}$ and $\pi_{1i}$ respectively. The
sample $A_2$ is a simple random sample with $n_1 = 2000$. We compare five
different estimators for $\theta = E[Y]$.

\begin{itemize}
  \item[1.] Horvitz-Thompson estimator (HT): $\hat Y = N^{-1} \sum_{i \in A_0}
    \frac{y_i}{\pi_{0i}}$,
  \item[2.] Non-nested regression (NNReg): This is the non-nested regression from
    Equation~\eqref{eq:nnopt} with only using information from Samples $A_0$ and
    $A_1$,
  \item[3.] Multi-Source proposed (MSEst): This is the proposed estimator from
    Equation~\eqref{eq:dc3},
  \item[4.] Multi-Source population (MSPop): This is the proposed estimator with
    using the true value of $T_1$ from the population,
  \item[5.] Multi-Source regression (MSReg): This is the linearized regression
    estimator from FIXME.
\end{itemize}

\begin{table}[ht!]
  \centering
  \input{tables/msdcsim1.tex}
% This table was generated from ../../src/explore/20240506-msdcsim.qmd
\caption{This table shows the results of Simulation Study 2. It displays the
Bias, RMSE, empirical 95\% confidence interval, and a t-statistic assessing the
unbiasedness of each estimator for the estimators: HT, NNReg, MSPop, MSEst, and
MSReg.}
\label{tab:msdc-mean}
\end{table}

As expected MSPop has the lowest RMSE because it also uses the population
totals. It seems like MSEst and MSReg are almost equivalent, which is good
because they are also supposed to be identical. The MSEst estimator outperforms
NNReg because it also uses information from $A_2$, even though it implicitly
uses a regression estimator with $X_3$ as a covariate, which is unnecessary.

@@

Building off of the previous simulation study, we now consider the case for
which we observe $Y$ in separate samples.
We have the following superpopulation model with $N = 10,000$ elements:

$$
\begin{aligned}
X_{1i} &\stackrel{ind}{\sim} N(2, 1) \\
X_{2i} &\stackrel{ind}{\sim} Unif(0, 4) \\
X_{3i} &\stackrel{ind}{\sim} N(5, 1) \\
\varepsilon_i &\stackrel{ind}{\sim} N(0, 1) \\
Y_{i} &= 3 X_{1i} + 2 X_{2i} + \varepsilon_i \\
\pi_{A1i} &= \min(\max(\Phi(-x_{1i}), 0.02), 0.9)\\
\pi_{A2i} &= \min(\max(\Phi(x_{3i} - 6), 0.02), 0.95) \\
\pi_{B1i} &= n_1 / N\\
\pi_{B2i} &= \Phi(x_{2i} - 2) \\
\end{aligned}
$$

We observe the following columns in each sample

\begin{table}[ht!]
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    Sample & $X_1$ & $X_2$ & $X_3$ & $Y$ \\
    \midrule
   $A_1$  & \checkmark     & \checkmark     & \checkmark     &  \checkmark \\    
   $A_2$  & \checkmark     & & \checkmark     &  \checkmark \\    
   $B_1$  & \checkmark     &       & \checkmark     &    \\  
   $B_2$  & \checkmark     & \checkmark     &       &    \\  
   \bottomrule
  \end{tabular}
\end{table}

For the sampling mechanism $A_1$, $A_2$ and $B_2$ are selected using a Poisson
sample with response probabilities $\pi_{A1i}$, $\pi_{A2i}$ and $\pi_{B1i}$
respectively. The $B_2$ sample is a simple random sample (SRS). We estimate the
following methods:

\begin{itemize}
  \item[1.] Horvitz-Thompson estimator for $A_1$ (HTA1):

    $$\hat Y_{HT, A_1} = \sum_{i \in A_1} \frac{y_i}{\pi_{A1i}}.$$
  \item[2.] Horvitz-Thompson estimator for $A_2$ (HTA1):
    $$\hat Y_{HT, A_2} = \sum_{i \in A_2} \frac{y_i}{\pi_{A2i}}.$$
  \item[3.] Weighted Horvitz-Thompson estimator (WHT):
    $$\hat Y_{WHT} = \frac{\hat Y_{HT, A_1} / \hat V_{A_1} + \hat Y_{HT, A_2} /
    \hat V_{A_2}}{1 / \hat V_{A_1} + 1 / \hat V_{A_2}}$$

    where $\hat V_{A_m}$ is the estimated variance of the Horvitz-Thompson
    estimator $\hat Y_{HT, A_m}$.
  \item[4.] Multi-Source proposed (MSEst): This is the proposed estimator from
    Equation~FIXME.
  \item[5.] Multi-Source population (MSPop): This is the proposed estimator with
    using the true value of $T_1$ from the population,
  \item[6.] Multi-Source regression (MSReg): This is the linearized regression
    estimator from FIXME.
\end{itemize}

\begin{table}[ht!]
  \centering
  \input{tables/msdcsim2.tex}
% This table was generated from ../../src/explore/20240511-msdcsim2.qmd
\caption{This table shows the results of Simulation Study 2. It displays the
Bias, RMSE, empirical 95\% confidence interval, and a t-statistic assessing the
unbiasedness of each estimator for the estimators: HT, NNReg, MSPop, MSEst, and
MSReg.}
\label{tab:msdc2-mean}
\end{table}

% FIXME: Change to GLS estimate of Y.

@@

\end{document}

### 2024-05-13 src/explore/20240506-msdcsim.qmd
Fixed multisource simulation 2. It works, but I need to change the estimator to be a GLS estimate instead of a simple average.

1. The $\pi^*$-estimator,
2. The two-phase regression estimator,
3. The debiased calibration estimator (with known finite population total), and
4. The debiased calibration estimator with estimated population totals from the
   Phase 1 sample.

@@

N_obs <- 10000
n1_obs <- 1000
n2_obs <- 2000

library(dplyr)
library(GECal)
library(nleqslv)
library(doParallel)
library(doRNG)
library(CVXR)
library(rlang)

@@

$$
\begin{aligned}
X_{1i} &\stackrel{ind}{\sim} N(2, 1) \\
X_{2i} &\stackrel{ind}{\sim} Unif(0, 4) \\
X_{3i} &\stackrel{ind}{\sim} N(0, 1) \\
X_{4i} &\stackrel{ind}{\sim} Unif(0.1, 0.9) \\
\varepsilon_i &\stackrel{ind}{\sim} N(0, 1) \\
Y_{i} &= 3 X_{1i} + 2 X_{2i} + \varepsilon_i \\
\pi_{0i} &= \Phi(-x_{1i} - 2)\\
\pi_{1i} &= |x_{1i}| / \sum_{i \in U} |x_{i1}|\\
\pi_{2i} &= n_2 / N.\\
\end{aligned}
$$

@@

| Sample | $X_1$ | $X_2$ | $X_3$ |  $Y$ |
|:-------|------:|------:|------:|-----:|
| $A_0$  | ✓     | ✓     | ✓     |  ✓   |  
| $A_1$  | ✓     | ✓     |       |      |  
| $A_2$  | ✓     |       | ✓     |      |

@@

gen_pop <- function(obs) {

  x1 <- rnorm(obs, 2, 1)
  x2 <- runif(obs, 0, 4)
  x3 <- rnorm(obs, 0, 1)
  x4 <- runif(obs, 0.1, 0.9)
  eps <- rnorm(obs)

@@

  return(tibble(X1 = x1, X2 = x2, X3 = x3, X4 = x4, Y = y))
}

#' This function adds sampling probabilites to a population data frame.
#'
#' @details The phase 2 formula will be included for every element. There is no
#' information about if an element is part of the Phase 1 or Phase 2 sample.
update_pop <- function(pop_df, p0_formula, p1_formula, p2_formula) {

  pi0 <- eval(parse_expr(p0_formula))
  pi1 <- eval(parse_expr(p1_formula))
  pi2 <- eval(parse_expr(p2_formula))

  pop_df %>%
    mutate(pi0 = pi0, pi1 = pi1, pi2 = pi2)
}

#' This function generates Phase 1 and Phase 2 samples from an updated
#' population with selection probabilites.
gen_samps <- function(upop_df, p0_type, p1_type, p2_type) {

  if (p0_type == "poisson") {
    del0 <- rbinom(nrow(upop_df), 1, upop_df$pi0)
  } else if (p1_type == "srs") {
    ind <- sample(1:nrow(upop_df), size = upop_df$pi0[1] * nrow(upop_df))
    del0 <- as.numeric(1:nrow(upop_df) %in% ind)
  } else {
    stop("We have only implemented poisson and srs for Sample 0.")
  }

  p0_df <- mutate(upop_df, del0 = del0) %>% filter(del0 == 1)

  if (p1_type == "poisson") {
    del1 <- rbinom(nrow(upop_df), 1, upop_df$pi1)
  } else if (p1_type == "srs") {
    ind <- sample(1:nrow(upop_df), size = upop_df$pi1[1] * nrow(upop_df))
    del1 <- as.numeric(1:nrow(upop_df) %in% ind)
  } else {
    stop("We have only implemented poisson and srs for Sample 1.")
  }

  p1_df <- mutate(upop_df, del1 = del1) %>% filter(del1 == 1)

  if (p2_type == "poisson") {
    del2 <- rbinom(nrow(upop_df), 1, upop_df$pi2)
  } else if (p2_type == "srs") {
    ind <- sample(1:nrow(upop_df), size = round(upop_df$pi2[1] * nrow(upop_df)))
    del2 <- as.numeric(1:nrow(upop_df) %in% ind)
  } else {
    stop("We have only implemented poisson and srs for Sample 2.")
  }

  p2_df <- mutate(upop_df, del2 = del2) %>% filter(del2 == 1)

@@

@@

>>>>

1. The a HT-estimator,
2. The non-nested two-phase regression estimator ($A_0$ and $A_2$),
3. The debiased calibration estimator (with known finite population total), and
4. The debiased calibration estimator with estimated population totals from the
   Phase 1 sample.

@@

N_obs <- 10000
n1_obs <- 2000

library(dplyr)
library(nleqslv)
library(doParallel)
library(doRNG)

@@

$$
\begin{aligned}
X_{1i} &\stackrel{ind}{\sim} N(2, 1) \\
X_{2i} &\stackrel{ind}{\sim} Unif(0, 4) \\
X_{3i} &\stackrel{ind}{\sim} N(0, 1) \\
Z_i &\stackrel{ind}{\sim} N(0, 1) \\
\varepsilon_i &\stackrel{ind}{\sim} N(0, 1) \\
Y_{i} &= 3 X_{1i} + 2 X_{2i} + \varepsilon_i \\
\pi_{0i} &= \min(\max(\Phi(-x_{1i}), 0.02), 0.9)\\
\pi_{1i} &= n_1 / N\\
\pi_{2i} &= \Phi(x_{2i} - 2) \\
\end{aligned}
$$

@@

| Sample | $X_1$ | $X_2$ | $X_3$ |  $Y$ |
|:-------|------:|------:|------:|-----:|
| $A_0$  | ✓     | ✓     | ✓     |  ✓   |  
| $A_1$  | ✓     |       | ✓     |      |  
| $A_2$  | ✓     | ✓     |       |      |

@@

gen_pop <- function(N_obs, n1_obs) {

  x1 <- rnorm(N_obs, 2, 1)
  x2 <- runif(N_obs, 0, 4)
  x3 <- rnorm(N_obs, 5, 1)
  z <- rnorm(N_obs, 0, 1)

  eps <- rnorm(N_obs)

@@

  pi0 <- pmin(pmax(pnorm(-x1), 0.02), 0.9)
  # pi1 <- pnorm(-z - 1) # Informative sampling. Do we want this?
  pi1 <- n1_obs / N_obs
  # pi2 <- pmin(pmax(pnorm(x2 - 4), 0.01), 0.9)
  pi2 <- pnorm(x2 - 2)

  return(tibble(X1 = x1, X2 = x2, X3 = x3, Y = y,
                pi0 = pi0, pi1 = pi1, pi2 = pi2))
}

#' This function generates Phase 1 and Phase 2 samples from an updated
#' population with selection probabilites.
gen_samps <- function(pop_df, p0_type, p1_type, p2_type) {

  if (p0_type == "poisson") {
    del0 <- rbinom(nrow(pop_df), 1, pop_df$pi0)
  } else if (p0_type == "srs") {
    ind <- sample(1:nrow(pop_df), size = pop_df$pi0[1] * nrow(pop_df))
    del0 <- as.numeric(1:nrow(pop_df) %in% ind)
  } else {
    stop("We have only implemented poisson and srs for Sample 0.")
  }

  p0_df <- mutate(pop_df, del0 = del0) %>% filter(del0 == 1)

  if (p1_type == "poisson") {
    del1 <- rbinom(nrow(pop_df), 1, pop_df$pi1)
  } else if (p1_type == "srs") {
    ind <- sample(1:nrow(pop_df), size = pop_df$pi1[1] * nrow(pop_df))
    del1 <- as.numeric(1:nrow(pop_df) %in% ind)
  } else {
    stop("We have only implemented poisson and srs for Sample 1.")
  }

  p1_df <- mutate(pop_df, del1 = del1) %>% filter(del1 == 1)

  if (p2_type == "poisson") {
    del2 <- rbinom(nrow(pop_df), 1, pop_df$pi2)
  } else if (p2_type == "srs") {
    ind <- sample(1:nrow(pop_df), size = round(pop_df$pi2[1] * nrow(pop_df)))
    del2 <- as.numeric(1:nrow(pop_df) %in% ind)
  } else {
    stop("We have only implemented poisson and srs for Sample 2.")
  }

  p2_df <- mutate(pop_df, del2 = del2) %>% filter(del2 == 1)

@@

ht_est <- function(p0_df, N_obs, p0_type = "poisson") {

  theta <- sum(p0_df$Y / p0_df$pi0) / N_obs

  if (p0_type == "poisson") {

    v_hat <- sum((1 - p0_df$pi0) / p0_df$pi0^2 * p0_df$Y^2) / N_obs^2

  } else {

    v_hat <- NA

  }

  return(list(theta = theta, v_hat = v_hat))
}

reg_est <- function(p0_df, p1_df, N_obs, p0_samp = "poisson", p1_samp = "srs") {

  v_poisson <- sum((1 - p0_df$pi0) / p0_df$pi0^2 * p0_df$Y^2) / N_obs^2
  v_srs <- (1 / nrow(p0_df) - 1 / N_obs) * var(p0_df$Y)
  d_eff <- v_poisson / v_srs
  n0_eff <- nrow(p0_df) / d_eff
  n1_eff <- nrow(p1_df)

  x1_hat <- 
    c(sum(p1_df$X1 / p1_df$pi1) / N_obs,
      sum(p1_df$X2 / p1_df$pi1) / N_obs)

  x0_hat <- 
    c(sum(p0_df$X1 / p0_df$pi0) / N_obs,
      sum(p0_df$X2 / p0_df$pi0) / N_obs)

  w <- n1_eff / (n1_eff + n0_eff)
  xc_hat <- (n1_eff * x1_hat + n0_eff * x0_hat) / (n1_eff + n0_eff)

  # Estimate beta
  mod <- lm(Y ~ X1 + X2, data = p0_df)

  # Regression Estimation
  y_ht <- sum(p0_df$Y / p0_df$pi0) / N_obs
  theta <- y_ht + sum((xc_hat - x0_hat) * mod$coefficients[2:3])

  # Variance Estimation
  coefs <- mod$coefficients
  eps <- (p0_df$Y - coefs[1] * w - coefs[2] * w * p0_df$X1 - coefs[3] * w * p0_df$X2)
  var_x <- 
  (1 / nrow(p1_df) - 1 / N_obs) * var(matrix(c(p1_df$X1, p1_df$X2), ncol = 2))

  v1 <- w^2 * matrix(coefs[2:3], nrow = 1) %*% var_x %*% matrix(coefs[2:3], ncol = 1)
  v2 <- sum((1 - p0_df$pi0) / p0_df$pi0^2 * eps^2) / N_obs^2

  cov_xy <- c(sum((1 - p0_df$pi0) / p0_df$pi0^2 * coefs[2] * 
                 (n0_eff) / (n1_eff + n0_eff) * p0_df$X1 * eps) / N_obs^2,
              sum((1 - p0_df$pi0) / p0_df$pi0^2 * coefs[3] * 
                 (n0_eff) / (n1_eff + n0_eff) * p0_df$X3 * eps) / N_obs^2)
  v3 <- sum(cov_xy)

  v_hat <- v1 + v2 + v3

  return(list(theta = theta, v_hat = as.numeric(v_hat)))
}

#' This  function does the debiased calibration
#'
#' @param zmat - A n x p matrix
#' @param w1i - A vector of length n
#' @param d2i - A vector of length n
#' @param T1 - A vector of length p
#' @param qi - A scaler or a vector of length n
#' @param entropy - One of "EL", "ET"
solveGE <- function(zmat, w1i, d2i, T1, qi, entropy) {

  f <- function(lam, zmat, w1i, d2i, T1, qi, entropy, returnw = FALSE) {

    if (entropy == "EL") {
      w <- -d2i / drop(zmat %*% lam)
    } else if (entropy == "ET") {
      w <- d2i * exp(drop(zmat %*% lam))
    } else {
      stop("We only accept entropy of EL or ET.")
    }

    if (returnw) {
      return(w)
    } else {
      return(drop((w * w1i * qi) %*% zmat) - T1)
    }
  }

  j <- function(lam, zmat, w1i, d2i, T1, qi, entropy) {
    if (entropy == "EL") {
      res <- t(zmat) %*% diag((w1i * qi * d2i) / drop(zmat %*% lam)^2) %*% zmat
    } else if (entropy == "ET") {
      res <- t(zmat) %*% diag((w1i * qi * d2i) * exp(drop(zmat %*% lam))) %*% zmat
    }

    return(res)
  }

  init <- c(rep(0, ncol(zmat) - 1), 1)
  res <- 
  nleqslv(init, f, jac = j, zmat = zmat, w1i = w1i, d2i = d2i,
          T1 = T1, qi = qi, entropy = entropy,
          method = "Newton", control = list(maxit = 1e5, allowSingular = TRUE))

  resw <- f(res$x, zmat, w1i, d2i, T1, qi, entropy, returnw = TRUE)

  if (!(res$termcd %in% c(1))) {
    return(NA)
  }

  return(resw)

}

dc_ms_ybar <- 
  function(p0_df, p1_df, p2_df, pop_df, estT1, qi = 1, entropy = "EL", reg = FALSE) {

  d_vec <- 1 / (p0_df$pi0)
  if (entropy == "EL") {
    gdi <- -1 / d_vec
    gdip <- -1 / (1 / pop_df$pi0)
    gpinv <- d_vec^2
  } else if (entropy == "ET") {
    gdi <- log(d_vec)
    gdip <- log(1 / pop_df$pi0)
    gpinv <- d_vec
  } else {
    stop("This type of entropy has not yet been implemented.")
  }

  samp_X <- cbind(rep(1, nrow(p0_df)), as.matrix(select(p0_df, X1, X2, X3)))
  zmat <- cbind(samp_X, gdi)
  w1i <- 1
  d0i <- 1 / p0_df$pi0

  if (estT1) {
    x1_0 <- sum(p0_df$X1 / p0_df$pi0) / N_obs
    x2_0 <- sum(p0_df$X2 / p0_df$pi0) / N_obs
    x3_0 <- sum(p0_df$X3 / p0_df$pi0) / N_obs

    x1_1 <- sum(p1_df$X1 / p1_df$pi1) / N_obs
    x3_1 <- sum(p1_df$X3 / p1_df$pi1) / N_obs

    x1_2 <- sum(p2_df$X1 / p2_df$pi2) / N_obs
    x2_2 <- sum(p2_df$X2 / p2_df$pi2) / N_obs

    xhat <- c(x1_0, x2_0, x3_0, x1_1, x3_1, x1_2, x2_2)
    x_mat <- 
    matrix(c(1, 0, 0,
             0, 1, 0,
             0, 0, 1,
             1, 0, 0,
             0, 0, 1,
             1, 0, 0,
             0, 1, 0), ncol = 3, byrow = TRUE)
    vmat <- matrix(0, nrow = 7, ncol = 7)
    vmat[1, 1] <- sum((1 / p0_df$pi0^2 - 1 / p0_df$pi0) * p0_df$X1^2) / nrow(pop_df)^2
    vmat[1, 2] <- 
      sum((1 / p0_df$pi0^2 - 1 / p0_df$pi0) * p0_df$X1 * p0_df$X2) / nrow(pop_df)^2
    vmat[1, 3] <-
      sum((1 / p0_df$pi0^2 - 1 / p0_df$pi0) * p0_df$X1 * p0_df$X3) / nrow(pop_df)^2
    vmat[2, 1] <- vmat[1, 2]
    vmat[3, 1] <- vmat[1, 3]
    vmat[2, 2] <- sum((1 / p0_df$pi0^2 - 1 / p0_df$pi0) * p0_df$X2^2) / nrow(pop_df)^2
    vmat[2, 3] <-
      sum((1 / p0_df$pi0^2 - 1 / p0_df$pi0) * p0_df$X2 * p0_df$X3) / nrow(pop_df)^2
    vmat[3, 2] <- vmat[2, 3]
    vmat[3, 3] <- sum((1 / p0_df$pi0^2 - 1 / p0_df$pi0) * p0_df$X3^2) / nrow(pop_df)^2

    vmat[4, 4] <- (1 / nrow(p1_df) - 1 / nrow(pop_df)) * var(p1_df$X1)
    vmat[5, 5] <- (1 / nrow(p1_df) - 1 / nrow(pop_df)) * var(p1_df$X3)
    vmat[4, 5] <- (1 / nrow(p1_df) - 1 / nrow(pop_df)) * cov(p1_df$X1, p1_df$X3)
    vmat[5, 4] <- vmat[4, 5]

    vmat[6, 6] <- sum((1 / p2_df$pi2^2 - 1 / p2_df$pi2) * p2_df$X1^2) / nrow(pop_df)^2
    vmat[7, 7] <- sum((1 / p2_df$pi2^2 - 1 / p2_df$pi2) * p2_df$X2^2) / nrow(pop_df)^2
    vmat[6, 7] <- 
      sum((1 / p2_df$pi2^2 - 1 / p2_df$pi2) * p2_df$X1 * p2_df$X2) / nrow(pop_df)^2
    vmat[7, 6] <- vmat[6, 7]

    xgls <- drop(MASS::ginv(t(x_mat) %*% solve(vmat) %*% x_mat) %*% 
                (t(x_mat) %*% solve(vmat) %*% xhat))

    T1 <- c(nrow(pop_df),
            xgls[1] * nrow(pop_df),
            xgls[2] * nrow(pop_df),
            xgls[3] * nrow(pop_df),
            sum(gdip * qi))
  } else {
    T1 <- c(nrow(pop_df),
            sum(pop_df$X1),
            sum(pop_df$X2),
            sum(pop_df$X3),
            sum(gdip * qi))
  }

  dc_w <- solveGE(zmat, w1i, d0i, T1, qi, entropy)

  # Mean Estimation
  theta <- sum(p0_df$Y * dc_w * w1i) / nrow(pop_df)
  z_dc <- model.matrix(~1 + p0_df$X1 + p0_df$X2 + p0_df$X3 + gdi)
  gam_dc <- 
    solve(t(z_dc) %*% diag(d0i * gpinv * qi) %*% z_dc,
          t(z_dc) %*% diag(d0i * gpinv) %*% p0_df$Y)
  coefs <- as.numeric(gam_dc)
  u_mat <- 
  matrix(c(rep(1, nrow(p0_df)), p0_df$X1, p0_df$X2, p0_df$X3, gdi * qi), ncol = 5)
  eps <- (p0_df$Y - drop(u_mat %*% coefs))
  if (estT1) {
    # Variance Estimation
    # This is the variance of bar x gls not x gls total.
    var_x <- MASS::ginv(t(x_mat) %*% MASS::ginv(vmat) %*% x_mat)

    v1 <- matrix(coefs[2:4], nrow = 1) %*% var_x %*% matrix(coefs[2:4], ncol = 1)
    v2 <- sum((1 - p0_df$pi0) / p0_df$pi0^2 * eps^2) / nrow(pop_df)^2
    v_hat <- v1 + v2 
  } else {
    v2 <- sum((1 - p0_df$pi0) / p0_df$pi0^2 * eps^2) / nrow(pop_df)^2
    v_hat <- v2
  }
  if (reg) {
    theta <- 
    (drop(T1 %*% gam_dc) + 
      sum(1 / p0_df$pi0 * (p0_df$Y - drop(z_dc %*% gam_dc)))) / nrow(pop_df) 
  }

  return(list(theta = theta, v_hat = as.numeric(v_hat)))
}

@@

```{r}
#| label: run MCMC

set.seed(1)
pop_df <- gen_pop(N_obs, n1_obs)
true_theta <- mean(pop_df$Y)

clust <- makeCluster(min(detectCores() - 2, 100), outfile = "")
registerDoParallel(clust)

mc_res <- 
  foreach(iter=1:B_sims,
          .packages = c("dplyr", "nleqslv"),
          .options.RNG = 1) %dorng% {

    if (iter %% 100 == 0) {
      print(paste0("Iter: ", iter))
    }

    samps <- gen_samps(pop_df, "poisson", "srs", "poisson")
    p0_df <- samps[[1]]
    p1_df <- samps[[2]]
    p2_df <- samps[[3]]

    ht <- ht_est(p0_df, N_obs)
    reg <- reg_est(p0_df, p1_df, N_obs)
    ms_pop <- dc_ms_ybar(p0_df, p1_df, p2_df, pop_df, estT1 = FALSE)
    ms_est <- dc_ms_ybar(p0_df, p1_df, p2_df, pop_df, estT1 = TRUE)
    ms_reg <- dc_ms_ybar(p0_df, p1_df, p2_df, pop_df, estT1 = TRUE, reg = TRUE)

    return(tibble(Est = c("HT", "NNReg", "MSPop", "MSEst", "MSReg"),
                  Theta = c(ht[[1]], reg[[1]], ms_pop[[1]], ms_est[[1]], ms_reg[[1]]),
                  Var = c(ht[[2]], reg[[2]], ms_pop[[2]], ms_est[[2]], ms_reg[[2]]),
                  Iter = iter)
    )

  } %>% bind_rows()

stopCluster(clust)

```{r}
#| label: analyze results

# Check for failures
filter(mc_res, is.na(Theta))

# Analyze Mean
mc_res %>%
  mutate(err = Theta - true_theta) %>%
  mutate(CI = abs(err) < qnorm(0.975) * sqrt(Var)) %>%
  group_by(Est) %>%
  summarize(Bias = mean(err, na.rm = TRUE),
            RMSE = sqrt(mean(err^2, na.rm = TRUE)),
            EmpCI = mean(CI, na.rm = TRUE),
            sdest = sd(Theta, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(Ttest = abs(Bias) / sqrt(sdest^2 / B_sims)) %>%
  select(-sdest) %>%
  mutate(Ind = case_when(
    Est == "MSReg" ~ 5,
    Est == "MSEst" ~ 4,
    Est == "MSPop" ~ 3,
    Est == "NNReg" ~ 2,
    Est == "HT" ~ 1)
  ) %>%
  arrange(Ind) %>%
  select(Est, Bias, RMSE, EmpCI, Ttest) %>%
  knitr::kable("latex", booktabs = TRUE, digits = 4) %>%
  cat(file = "tables/msdcsim1.tex")
